---
title: "p8105_hw1_yc4195.Rmd"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents
## Problem1

```{r}
library(palmerpenguins)
library(ggplot2)
data("penguins", package = "palmerpenguins")
nrow(penguins)
ncol(penguins)
str(penguins)
summary(penguins)
#Write a short description of the penguins dataset (not the penguins_raw dataset) using inline R code: There are 8 variables: species, island,  bill_length_mm, bill_depth_mm , flipper_length_mm, body_mass_g, sex,year in this dataset. This dataset uses there species of penguins: Adelie,Chinstrap,Gentoo, and on three different islands: Biscoe, Dream, Torgersen from 2007 to 2009. The dataset has 344 rows and 8 columns. The mean flipper length is 200.9mm. 
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm ,color= species))+ geom_point()
ggsave("myplot.pdf")
```
#### Write a short description of the penguins dataset (not the penguins_raw dataset) using inline R code: There are 8 variables: species, island,  bill_length_mm, bill_depth_mm , flipper_length_mm, body_mass_g, sex,year in this dataset. This dataset uses there species of penguins: Adelie,Chinstrap,Gentoo, and on three different islands: Biscoe, Dream, Torgersen from 2007 to 2009. The dataset has 344 rows and 8 columns. The mean flipper length is 200.9mm. 


## Problem 2
```{r , eval=FALSE}
library(tidyverse)
la_df = tibble(
  norm_samp = rnorm(10),
  norm_samp_logical = norm_samp > 0,
  norm_samp_chr = c("A", "B", "D", "E","F", "G", "H", "I","J", "K"),
  norm_samp_factor = factor(c("low", "high", "medium", "high", "low", "medium", "high", "medium", "high", "low"))
)
mean(pull(la_df, norm_samp))
mean(pull(la_df, norm_samp_logical))
mean(pull(la_df, norm_samp_chr))
mean(pull(la_df, norm_samp_factor))
#the mean function works for the random sample and logical vector, but doesn't work for character vector and factor vector.

as.numeric(pull(la_df, norm_samp_logical))
as.numeric(pull(la_df, norm_samp_chr))
as.numeric(pull(la_df, norm_samp_factor))
# the "as.numeric" function works for logical vector and the factor vector, but it doesn't work for character vector.It's because if the factor is a number, transform it first to a character vector and then lead to a numeric value.If you try to convert an alphabet character to a numeric value, it will return NA. Also, the output of the logical vector returns TRUE (1) or False (0), which presents as numeric so the "as.numeric" function works.The factor vector has 3 different levels so the "as.numeric" function can work and assign them with different numbers.
```
#### the mean function works for the random sample and logical vector, but doesn't work for character vector and factor vector.

#### the "as.numeric" function works for logical vector and the factor vector, but it doesn't work for character vector.It's because if the factor is a number, transform it first to a character vector and then lead to a numeric value.If you try to convert an alphabet character to a numeric value, it will return NA. Also, the output of the logical vector returns TRUE (1) or False (0), which presents as numeric so the "as.numeric" function works.The factor vector has 3 different levels so the "as.numeric" function can work and assign them with different numbers.



